I have many people to thank for their invaluable advice and assistance which were crucial to the accomplishment of this project
\\
\indent First and foremost, I would like to express my sincere thanks to my supervisor, Mr. Craig Duffy, whose consistent support, insightful feedback, and guidance have been invaluable to me during this project.
His thought not only influenced this work, but also aided in my intellectual growth.
\\
\indent Also, I would like to express my gratitude to my second marker, Mr. Mark Rhodes, who I had the pleasure of meeting on Project-in-Progress Day.
His helpful feedback at that crucial stage gave me precise guidance on how to improve my project.
\\
\indent Additionally, I would like to thank Dr. Martin Serpell for his advice and guidance from the beginning of this project.
His advice was invaluable in selecting the project topic and his ongoing support has made the process much more enjoyable.
\\
\indent My friend, Mr. Kai Lim Ng, deserves special particular mention for his network-related expertise, which was required in setting up the email services for user registration and other application functionalities.
His technical support was vital for the project's accomplishment.
\\
\indent I am equally thankful to Ms. Kai Xin Phua for sharing her expertise in music classification. 
Her knowledge in music related field was essential in aligning the music recommendation system with the emotional analysis to enhance user experience.
\\
\indent My appreciation goes out to Ms. Megan Theng Ong, whose artistic abilities were instrumental in creating a visually striking and significant logo for the application. 
Her artistic contribution has greatly enhanced the project's UI and aesthetics.
\\
\indent Last but not least, I want to express my gratitude for my family's unwavering support, whose encouragement and belief in my capabilities have constantly motivated me during this journey.
 